---
title: "PA1_template.html"
author: "Abdoul Kader"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading and preprocessing the data
### Code


```{r}
activity <- read.csv("activity.csv")
summary(activity)

```

## What is mean total number of steps taken per day?
### 1. The total number of steps taken per day


```{r}
activityperdate <- aggregate(data=activity, steps~date, sum, na.rm = TRUE)
head(activityperdate)
```

### 2. Histogram  of the total number of steps taken each day

```{r}
hist(activityperdate$steps, xlab = "Steps")
```

### 3. Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean(activityperdate$steps)
median(activityperdate$steps)
```

## What is the average daily activity pattern?
### 1. Make a time series plot (i.e. type = "l"\color{red}{\verb|type = "l"|}type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
interval_per_stps <- aggregate(data=activity, steps~interval, mean, na.rm=TRUE)
with(interval_per_stps, plot(interval_per_stps$interval, interval_per_stps$steps, type = "l", xlab = "interval", ylab = "Steps"))
```


### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
interval_per_stps$interval[which.max(interval_per_stps$steps)]
```

## Imputing missing values
### 1. Calculate and report the total number of missing values in the dataset 

```{r}
sum((is.na(activity$steps)))
```

### 2. Devise a strategy for filling in all of the missing values in the dataset
We will replace NA’s with the mean for that 5-minute interval.
(Nous allons remplacer les NA avec la moyenne des intervalles 5-minute.)

### 3. New dataset that is equal to the original dataset but with the missing data filled in

```{r}
imputed_data <- activity
for (i in 1:length(imputed_data$steps)) {
   if (is.na(imputed_data$steps[i])) {
      imputed_data$steps[i] <- interval_per_stps$steps[interval_per_stps$interval == imputed_data$interval[i]]
   }
}
head(imputed_data)
```

### 4. histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day

```{r}
imp_steps_per_day <- aggregate(steps ~ date, imputed_data, sum, na.rm = TRUE)
sum(is.na(imp_steps_per_day$steps))
hist(imp_steps_per_day$steps, main = "Total Steps per day", xlab = "Steps")

mean(imp_steps_per_day$steps)

median(imp_steps_per_day$steps)
```

## Are there differences in activity patterns between weekdays and weekends?
### 1. New factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r}
imputed_data$date <- as.Date(imputed_data$date)
imputed_data$wkdy <- "weekday"
imputed_data$wkdy[weekdays(imputed_data$date) == "samedi" | weekdays(imputed_data$date) == "dimanche"] <- "weekend"
imputed_data$wkdy <- as.factor(imputed_data$wkdy)
```

### 2. Plot containing a time series plot


```{r}
imputed_data_interval <- aggregate(steps ~ interval + wkdy, imputed_data, mean, na.rm = TRUE)

library("ggplot2")
g <- ggplot(imputed_data_interval, aes(interval, steps))
g + facet_grid(wkdy ~ .) + geom_line() + ggtitle("Average number of steps per 5-min interval")

```
